On the eletrodynamic of moving bodies

### 2019-05-23 Article_AS.Rmd
Figure
Reulstats et discussion

Study sites (image)

@@

where yijkl  is the observation on the ijklth tree, $\mu$ is the overall mean, si is the fixed site effect, $b_{(i)j}$ is the fixed effect of the $j$ th bloc in site $i$, $f_k$ is the random effect of the k th family, $bf_{(i)j}$ is the random interaction of family and bloc, and $e_{ijkl} is the residual error.
In a full-sib design with random mating, members of the same family are presumed to share half of their genes (White et al., 2007). Therefore, individual heritability was obtained as follows:

>>>>

![legend of this figure](graph_table/parameters.png)

@@

where yijkl  is the observation on the ijklth tree, $\mu$ is the overall mean, si is the fixed site effect, $b_{(i)j}$ is the fixed effect of the $j$ th bloc in site $i$, $f_k$ is the random effect of the k th family, $bf_{(i)j}$ is the random interaction of family and bloc, and $e_{ijkl}$ is the residual error.
In a full-sib design with random mating, members of the same family are presumed to share half of their genes (White et al., 2007). Therefore, individual heritability was obtained as follows:
